---
title: "Print Tables"
author: "Enrico Benassi"
date: "August 2022"
output:
  html_document: default
  word_document: default
  pdf_document: default
font-family: Serif
fontsize: 12pt
linestretch: 1.2
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
  \floatplacement{table}{H}

---

<style>
body, p {
  background-color: white;
  color: black; 
  font-family: Times New Roman;
}
</style>

```{r setup, include=FALSE}
# this sets the default options for the document 
# echo = F tells R Markdown not to print the code
# the other settings tell R Markdown not to print out errors, warnings and messages 
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F, 
                      out.width = "70%", fig.align = "center")

# you need to load the R packages you are using
# if these aren't installed you will need to install them first
library(tidyverse)
library(pander)
library(arsenal)
library(texreg)
library(ggeffects)
library(fixest)
library(kableExtra)

# load the datasets -----

# Sample code. Actual code should be consistent with writexl location from 20220815_Data_Preparation_vF
dbhFE <- read_csv2("~/dbhFE1.TXT")
dbhFE <- dbhFE %>% mutate(cell= paste(cell, Region, Position)) # cell= paste(SizeClass, ATECO07,WorkTime, AgeGroup, Sex, Region, Position)

dbh5 <- dbhFE %>% filter(as.numeric(SizeClass) >= 2 & as.numeric(SizeClass) <= 5) %>% 
  mutate(SizeL=ifelse(as.numeric(SizeClass)>=4,1,0))

# DID Models CELL FE AND MONTH and YEAR FE ----

FEdTDC2 <- feols(log(FTC+OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh5)

FEdOEC2 <- feols(log(OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh5)

FEdFTC2 <- feols(log(FTC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh5)

FEdOECShare2 <- feols(OECShare ~
                        fa+jahi+jao+dd+SizeL+ 
                        fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                      | Region + cell + Year.y + Month,
                      data = dbh5)

# DID MODEL Driscoll Kraay FE -----

FEdTDCDK <- feols(log(FTC+OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 panel.id = ~cell + TimeM,
                 vcov = "DK",
                 data = dbh5)

FEdOECDK <- feols(log(OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 panel.id = ~cell + TimeM,
                 vcov = "DK",
                 data = dbh5)

FEdFTCDK <- feols(log(FTC+1) ~
                    fa+jahi+jao+dd+SizeL+ 
                    fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                  | Region + cell + Year.y + Month,
                  panel.id = ~cell + TimeM,
                  vcov = "DK",
                  data = dbh5)

FEdOECShareDK <- feols(OECShare ~
                        fa+jahi+jao+dd+SizeL+ 
                        fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                      | Region + cell + Year.y + Month,
                      panel.id = ~cell + TimeM,
                      vcov = "DK",
                      data = dbh5)

# DID MODEL Newey West FE ----

FEdTDCNW <- feols(log(FTC+OEC+1) ~
                    fa+jahi+jao+dd+SizeL+ 
                    fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                  | Region + cell + Year.y + Month,
                  panel.id = ~cell + TimeM,
                  vcov = "NW",
                  data = dbh5)

FEdOECNW <- feols(log(OEC+1) ~
                    fa+jahi+jao+dd+SizeL+ 
                    fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                  | Region + cell + Year.y + Month,
                  panel.id = ~cell + TimeM,
                  vcov = "NW",
                  data = dbh5)

FEdFTCNW <- feols(log(FTC+1) ~
                    fa+jahi+jao+dd+SizeL+ 
                    fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                  | Region + cell + Year.y + Month,
                  panel.id = ~cell + TimeM,
                  vcov = "NW",
                  data = dbh5)

FEdOECShareNW <- feols(OECShare ~
                         fa+jahi+jao+dd+SizeL+ 
                         fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                       | Region + cell + Year.y + Month,
                       panel.id = ~cell + TimeM,
                       vcov = "NW",
                       data = dbh5)

# Placebo TEST -----

dbh6 <- dbhFE %>% filter(as.numeric(SizeClass) >= 10 & as.numeric(SizeClass) <= 11) %>% 
  mutate(SizeL=ifelse(as.numeric(SizeClass)>=11,1,0))

FEdTDCP <- feols(log(FTC+OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 
                 data = dbh6)

FEdOECP <- feols(log(OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh6)

FEdFTCP <- feols(log(FTC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh6)

FEdOECShareP <- feols(OECShare ~
                        fa+jahi+jao+dd+SizeL+ 
                        fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL
                      | Region + cell + Year.y + Month,
                      data = dbh6)

# Reference period dignitiy decree

dbh5 <- dbh5 %>% mutate(int=as.factor(int))
dbh5 <- within(dbh5, int <- relevel(factor(dbh5$int, ordered = FALSE), ref = "4"))
levels(dbh5$int)

FEdTDCDD <- feols(log(FTC+OEC+1) ~
                   int+SizeL+ 
                   int:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh5)

FEdOECDD <- feols(log(OEC+1) ~
                   int+SizeL+ 
                   int:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh5)

FEdFTCDD <- feols(log(FTC+1) ~
                    int+SizeL+ 
                    int:SizeL
                 | Region + cell + Year.y + Month,
                 data = dbh5)

FEdOECShareDD <- feols(OECShare ~
                         int+SizeL+ 
                         int:SizeL
                      | Region + cell + Year.y + Month,
                      data = dbh5)

# DID Models Interactions ----
## DID Interaction SEX ----

dbh5 <- within(dbh5, Sex <- relevel(factor(dbh5$Sex, ordered = FALSE), ref = "M"))

FEdTDCF <- feols(log(FTC+OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                   Sex + 
                   SizeL:Sex+
                   fa:Sex + jahi:Sex + jao:Sex + dd:Sex +
                   fa:SizeL:Sex+jahi:SizeL:Sex +jao:SizeL:Sex +dd:SizeL:Sex
                 | Region + cell + TimeM,
                 data = dbh5)

FEdOECF <- feols(log(OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   Sex + 
                   SizeL:Sex+
                   fa:Sex + jahi:Sex + jao:Sex + dd:Sex +
                   fa:SizeL:Sex+jahi:SizeL:Sex +jao:SizeL:Sex +dd:SizeL:Sex
                 | Region + cell + TimeM,
                 data = dbh5)

FEdFTCF <- feols(log(FTC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   Sex + 
                   SizeL:Sex+
                   fa:Sex + jahi:Sex + jao:Sex + dd:Sex +
                   fa:SizeL:Sex+jahi:SizeL:Sex +jao:SizeL:Sex +dd:SizeL:Sex
                 | Region + cell + TimeM,
                 data = dbh5)

FEdOECShareF <- feols(OECShare ~
                        fa+jahi+jao+dd+SizeL+ 
                        fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                        Sex + 
                        SizeL:Sex+
                        fa:Sex + jahi:Sex + jao:Sex + dd:Sex +
                        fa:SizeL:Sex+jahi:SizeL:Sex +jao:SizeL:Sex +dd:SizeL:Sex
                      | Region + cell + TimeM,
                      data = dbh5)

## DID Interaction AgeGroup ----

levels(factor(dbh5$AgeGroup))
dbh5 <- within(dbh5, AgeGroup <- relevel(factor(dbh5$AgeGroup, ordered = FALSE), ref = "55+"))


FEdTDCY <- feols(log(FTC+OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                   AgeGroup + 
                   SizeL:AgeGroup+
                   fa:AgeGroup + jahi:AgeGroup + jao:AgeGroup + dd:AgeGroup +
                   fa:SizeL:AgeGroup+jahi:SizeL:AgeGroup +jao:SizeL:AgeGroup +dd:SizeL:AgeGroup
                 | Region + cell + TimeM,
                 data = dbh5)

FEdOECY <- feols(log(OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   AgeGroup + 
                   SizeL:AgeGroup+
                   fa:AgeGroup + jahi:AgeGroup + jao:AgeGroup + dd:AgeGroup +
                   fa:SizeL:AgeGroup+jahi:SizeL:AgeGroup +jao:SizeL:AgeGroup +dd:SizeL:AgeGroup
                 | Region + cell + TimeM,
                 data = dbh5)

FEdFTCY <- feols(log(FTC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   AgeGroup + 
                   SizeL:AgeGroup+
                   fa:AgeGroup + jahi:AgeGroup + jao:AgeGroup + dd:AgeGroup +
                   fa:SizeL:AgeGroup+jahi:SizeL:AgeGroup +jao:SizeL:AgeGroup +dd:SizeL:AgeGroup
                 | Region + cell + TimeM,
                 data = dbh5)

FEdOECShareY <- feols(OECShare ~
                        fa+jahi+jao+dd+SizeL+ 
                        fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                        AgeGroup + 
                        SizeL:AgeGroup+
                        fa:AgeGroup + jahi:AgeGroup + jao:AgeGroup + dd:AgeGroup +
                        fa:SizeL:AgeGroup+jahi:SizeL:AgeGroup +jao:SizeL:AgeGroup +dd:SizeL:AgeGroup
                      | Region + cell + TimeM,
                      data = dbh5)


## DID Interaction Position Level ----

levels(factor(dbh5$Position))
dbh5 <- within(dbh5, Position <- relevel(factor(dbh5$Position, ordered = FALSE), ref = "High_WC"))


FEdTDCPL <- feols(log(FTC+OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                   Position + 
                   SizeL:Position+
                   fa:Position + jahi:Position + jao:Position + dd:Position +
                   fa:SizeL:Position+jahi:SizeL:Position +jao:SizeL:Position +dd:SizeL:Position
                 | Region + cell + TimeM,
                 data = dbh5)


FEdOECPL <- feols(log(OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   Position + 
                   SizeL:Position+
                   fa:Position + jahi:Position + jao:Position + dd:Position +
                   fa:SizeL:Position+jahi:SizeL:Position +jao:SizeL:Position +dd:SizeL:Position
                 | Region + cell + TimeM,
                 data = dbh5)

FEdFTCPL <- feols(log(FTC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   Position + 
                   SizeL:Position+
                   fa:Position + jahi:Position + jao:Position + dd:Position +
                   fa:SizeL:Position+jahi:SizeL:Position +jao:SizeL:Position +dd:SizeL:Position
                 | Region + cell + TimeM,
                 data = dbh5)

FEdOECSharePL <- feols(OECShare ~
                        fa+jahi+jao+dd+SizeL+ 
                        fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                        Position + 
                        SizeL:Position+
                        fa:Position + jahi:Position + jao:Position + dd:Position +
                        fa:SizeL:Position+jahi:SizeL:Position +jao:SizeL:Position +dd:SizeL:Position
                      | Region + cell + TimeM,
                      data = dbh5)

## DID Interaction GeoArea ----

dbh5 <- dbh5 %>% mutate(GeoArea= ifelse(Region=="VALLE D'AOSTA"|
                                             Region=="PIEMONTE"|
                                             Region=="LIGURIA"|
                                             Region=="LOMBARDIA"|
                                             Region=="EMILIA ROMAGNA"|
                                             Region=="VENETO"|
                                             Region=="FRIULI VENEZIA GIULIA"|
                                             Region=="TRENTINO ALTO ADIGE", "North",
                                           ifelse(Region=="PUGLIA"|
                                                    Region=="ABRUZZO"|
                                                    Region=="BASILICATA"|
                                                    Region=="CALABRIA"|
                                                    Region=="CAMPANIA"|
                                                    Region=="MOLISE"|
                                                    Region=="SARDEGNA"|
                                                    Region=="SICILIA","South and Islands",
                                                  "Central")))


levels(factor(dbh5$GeoArea))
dbh5 <- within(dbh5, GeoArea <- relevel(factor(dbh5$GeoArea, ordered = FALSE), ref = "North"))

FEdTDCG <- feols(log(FTC+OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                   GeoArea + 
                   SizeL:GeoArea+
                   fa:GeoArea + jahi:GeoArea + jao:GeoArea + dd:GeoArea +
                   fa:SizeL:GeoArea+jahi:SizeL:GeoArea +jao:SizeL:GeoArea +dd:SizeL:GeoArea
                 | Region + cell + TimeM,
                 data = dbh5)

FEdOECG <- feols(log(OEC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   GeoArea + 
                   SizeL:GeoArea+
                   fa:GeoArea + jahi:GeoArea + jao:GeoArea + dd:GeoArea +
                   fa:SizeL:GeoArea+jahi:SizeL:GeoArea +jao:SizeL:GeoArea +dd:SizeL:GeoArea
                 | Region + cell + TimeM,
                 data = dbh5)

FEdFTCG <- feols(log(FTC+1) ~
                   fa+jahi+jao+dd+SizeL+ 
                   fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                   GeoArea + 
                   SizeL:GeoArea+
                   fa:GeoArea + jahi:GeoArea + jao:GeoArea + dd:GeoArea +
                   fa:SizeL:GeoArea+jahi:SizeL:GeoArea +jao:SizeL:GeoArea +dd:SizeL:GeoArea
                 | Region + cell + TimeM,
                 data = dbh5)

FEdOECShareG <- feols(OECShare ~
                        fa+jahi+jao+dd+SizeL+ 
                        fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                        GeoArea + 
                        SizeL:GeoArea+
                        fa:GeoArea + jahi:GeoArea + jao:GeoArea + dd:GeoArea +
                        fa:SizeL:GeoArea+jahi:SizeL:GeoArea +jao:SizeL:GeoArea +dd:SizeL:GeoArea
                      | Region + cell + TimeM,
                      data = dbh5)


## DID Interaction Part-Time and Full Time ----

levels(factor(dbh5$WorkTime))
dbh5 <- within(dbh5, WorkTime <- relevel(factor(dbh5$WorkTime, ordered = FALSE), ref = "F"))

FEdTDCPT <- feols(log(FTC+OEC+1) ~
                    fa+jahi+jao+dd+SizeL+ 
                    fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                    WorkTime + 
                    SizeL:WorkTime+
                    fa:WorkTime + jahi:WorkTime + jao:WorkTime + dd:WorkTime +
                    fa:SizeL:WorkTime+jahi:SizeL:WorkTime +jao:SizeL:WorkTime +dd:SizeL:WorkTime
                  | Region + cell + TimeM,
                  data = dbh5)


FEdOECPT <- feols(log(OEC+1) ~
                    fa+jahi+jao+dd+SizeL+ 
                    fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                    WorkTime + 
                    SizeL:WorkTime+
                    fa:WorkTime + jahi:WorkTime + jao:WorkTime + dd:WorkTime +
                    fa:SizeL:WorkTime+jahi:SizeL:WorkTime +jao:SizeL:WorkTime +dd:SizeL:WorkTime
                  | Region + cell + TimeM,
                  data = dbh5)

FEdFTCPT <- feols(log(FTC+1) ~
                    fa+jahi+jao+dd+SizeL+ 
                    fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL +
                    WorkTime + 
                    SizeL:WorkTime+
                    fa:WorkTime + jahi:WorkTime + jao:WorkTime + dd:WorkTime +
                    fa:SizeL:WorkTime+jahi:SizeL:WorkTime +jao:SizeL:WorkTime +dd:SizeL:WorkTime
                  | Region + cell + TimeM,
                  data = dbh5)

FEdOECSharePT <- feols(OECShare ~
                         fa+jahi+jao+dd+SizeL+ 
                         fa:SizeL+jahi:SizeL +jao:SizeL +dd:SizeL+
                         WorkTime + 
                         SizeL:WorkTime+
                         fa:WorkTime + jahi:WorkTime + jao:WorkTime + dd:WorkTime +
                         fa:SizeL:WorkTime+jahi:SizeL:WorkTime +jao:SizeL:WorkTime +dd:SizeL:WorkTime
                       | Region + cell + TimeM,
                       data = dbh5)


```


# DiD General Model 

Table 4
```{r results = "asis"}

GM1 <- htmlreg(list(FEdTDC2,FEdOEC2,FEdFTC2,FEdOECShare2), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                                "jahi:SizeL"="Hiring Incentives X Large Firms",
                                "jao:SizeL"="Jobs Act only X Large Firms",
                                "dd:SizeL"="Dignity Decree X Large Firms"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 | Post-reforms coefficients excluded from the table",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")))  

kbl(GM1, escape = F, align = "c")

```



# DiD Robustness models

Table 12 - Driscoll-Kraay SE

```{r results = "asis"}

DK <- htmlreg(list(FEdTDCDK,FEdOECDK,FEdFTCNW,FEdOECShareDK), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                               "jahi:SizeL"="Hiring Incentives X Large Firms",
                               "jao:SizeL"="Jobs Act only X Large Firms",
                               "dd:SizeL"="Dignity Decree X Large Firms"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 | Post-reforms coefficients excluded from the table",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               # "Region SE Clustering" = c("YES","YES","YES","YES"),
                               "Driscoll Kraay SE" = c("YES","YES","YES","YES")))    

kbl(DK, escape = F, align = "c")
```

Table 13 - Newey-West SE

```{r results = "asis"}


NW <- htmlreg(list(FEdTDCNW,FEdOECNW,FEdFTCNW,FEdOECShareNW), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                               "jahi:SizeL"="Hiring Incentives X Large Firms",
                               "jao:SizeL"="Jobs Act only X Large Firms",
                               "dd:SizeL"="Dignity Decree X Large Firms"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 | Post-reforms coefficients excluded from the table",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               # "Region SE Clustering" = c("YES","YES","YES","YES"),
                               "Newey West SE" = c("YES","YES","YES","YES")))    

kbl(NW, escape = F, align = "c")
```

Table 11 - Placebo Tests

```{r results = "asis"}

PT <- htmlreg(list(FEdTDCP,FEdOECP,FEdFTCP,FEdOECShareP), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X >200 Employees Firms",
                               "jahi:SizeL"="Hiring Incentives X >200 Employees Firms",
                               "jao:SizeL"="Jobs Act only X >200 Employees Firms",
                               "dd:SizeL"="Dignity Decree X >200 Employees Firms"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 | Post-reforms coefficients excluded from the table",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")))   

kbl(PT, escape = F, align = "c")
```

Table 14 - Reference period Dignity Decree

```{r results = "asis"}

DD <- htmlreg(list(FEdTDCDD,FEdOECDD,FEdFTCDD,FEdOECShareDD), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("int0:SizeL"="Pre-Fornero X Large Firms",
                               "int1:SizeL"="Fornero Reform X Large Firms",
                               "int2:SizeL"="Hiring Incentives X Large Firms",
                               "int3:SizeL"="Jobs Act only X Large Firms",
                               "int4:SizeL"="Dignity Decree X Large Firms"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |**Dignity Decree Period as reference point** | Post-reforms coefficients excluded from the table",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")))  


kbl(DD, escape = F, align = "c")
```


# DiD Interaction Models

## Did Interactions with Sex

Table 15

```{r results = "asis"}
### Table Sex interaction  -----

SI <- htmlreg(list(FEdTDCF,FEdOECF,FEdFTCF,FEdOECShareF), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                               "jahi:SizeL"="Hiring Incentives X Large Firms",
                               "jao:SizeL"="Jobs Act only X Large Firms",
                               "dd:SizeL"="Dignity Decree X Large Firms",
                               "fa:SizeL:SexF"="Fornero Reform X Large Firms X Female",
                               "jahi:SizeL:SexF"="Hiring Incentives X Large Firms X Female",
                               "jao:SizeL:SexF"="Jobs Act only X Large Firms X Female",
                               "dd:SizeL:SexF"="Dignity Decree X Large Firms X Female"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |Post-reforms and interactions sex-reforms interactions excluded from the table 
        |Male category is excluded as it is the reference group",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")))
 

kbl(SI, escape = F, align = "c")
```

## Did Interactions with Age Groups

Table 16

```{r results = "asis"}

### Table AgeGroup interaction  -----

AI <- htmlreg(list(FEdTDCY,FEdOECY,FEdFTCY,FEdOECShareY), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                               "jahi:SizeL"="Hiring Incentives X Large Firms",
                               "jao:SizeL"="Jobs Act only X Large Firms",
                               "dd:SizeL"="Dignity Decree X Large Firms",
                               "fa:SizeL:AgeGroup<35"="Fornero Reform X Large Firms X Young",
                               "jahi:SizeL:AgeGroup<35"="Hiring Incentives X Large Firms X Young",
                               "jao:SizeL:AgeGroup<35"="Jobs Act only X Large Firms X Young",
                               "dd:SizeL:AgeGroup<35"="Dignity Decree X Large Firms X Young",
                               
                               "fa:SizeL:AgeGroup35-54"="Fornero Reform X Large Firms X Prime Age",
                               "jahi:SizeL:AgeGroup35-54"="Hiring Incentives X Large Firms X Prime Age",
                               "jao:SizeL:AgeGroup35-54"="Jobs Act only X Large Firms X Prime Age",
                               "dd:SizeL:AgeGroup35-54"="Dignity Decree X Large Firms X Prime Age"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |Post-reforms and interactions age-reforms interactions excluded from the table 
        |old age age category (55+ years) is excluded as it is the reference group",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")))  
 
kbl(AI, escape = F, align = "c")

```

## Did Interactions with Geo Area

Table 17

```{r results = "asis"}

### Table Geo Area interaction  -----

GI <- htmlreg(list(FEdTDCG,FEdOECG,FEdFTCG,FEdOECShareG), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                               "jahi:SizeL"="Hiring Incentives X Large Firms",
                               "jao:SizeL"="Jobs Act only X Large Firms",
                               "dd:SizeL"="Dignity Decree X Large Firms",
                               
                               "fa:SizeL:GeoAreaSouth and Islands"="Fornero Reform X Large Firms X South and Islands",
                               "jahi:SizeL:GeoAreaSouth and Islands"="Hiring Incentives X Large Firms X South and Islands",
                               "jao:SizeL:GeoAreaSouth and Islands"="Jobs Act only X Large Firms X South and Islands",
                               "dd:SizeL:GeoAreaSouth and Islands"="Dignity Decree X Large Firms X South and Islands",
                               
                               "fa:SizeL:GeoAreaCentral"="Fornero Reform X Large Firms X Central Italy",
                               "jahi:SizeL:GeoAreaCentral"="Hiring Incentives X Large Firms X Central Italy",
                               "jao:SizeL:GeoAreaCentral"="Jobs Act only X Large Firms X Central Italy",
                               "dd:SizeL:GeoAreaCentral"="Dignity Decree X Large Firms X Central Italy"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |Post-reforms and interactions area-reforms interactions excluded from the table 
        |North regions category is excluded as it is the reference group",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES"))) 
 
kbl(GI, escape = F, align = "c")

```


## Did Interactions with Position Level

Table 18

```{r results = "asis"}

### Table Position Level interaction  -----

PI <- htmlreg(list(FEdTDCPL,FEdOECPL,FEdFTCPL,FEdOECSharePL), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                               "jahi:SizeL"="Hiring Incentives X Large Firms",
                               "jao:SizeL"="Jobs Act only X Large Firms",
                               "dd:SizeL"="Dignity Decree X Large Firms",
                               
                               "fa:SizeL:PositionBlueCollar"="Fornero Reform X Large Firms X Blue Collar",
                               "jahi:SizeL:PositionBlueCollar"="Hiring Incentives X Large Firms X Blue Collar",
                               "jao:SizeL:PositionBlueCollar"="Jobs Act only X Large Firms X Blue Collar",
                               "dd:SizeL:PositionBlueCollar"="Dignity Decree X Large Firms X Blue Collar",
                               
                               "fa:SizeL:PositionWhiteCollar"="Fornero Reform X Large Firms X White Collar",
                               "jahi:SizeL:PositionWhiteCollar"="Hiring Incentives X Large Firms X White Collar",
                               "jao:SizeL:PositionWhiteCollar"="Jobs Act only X Large Firms X White Collar",
                               "dd:SizeL:PositionWhiteCollar"="Dignity Decree X Large Firms X White Collar"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |Post-reforms and interactions position-reforms interactions excluded from the table 
        |High white collar category is excluded as it is the reference group",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")))
 
kbl(PI, escape = F, align = "c")

```

## Did Interactions with Work Time

Table 19

```{r results = "asis"}

### Table Geo Area interaction  -----

### Table Part Time interaction  -----

WI <- htmlreg(list(FEdTDCPT,FEdOECPT,FEdFTCPT,FEdOECSharePT), 
        digits =3,
        custom.model.names = c("Hirings Growth", "OECs Growth", "FTCs Growth", "OEC Share"),
        custom.coef.map = list("fa:SizeL"="Fornero Reform X Large Firms",
                               "jahi:SizeL"="Hiring Incentives X Large Firms",
                               "jao:SizeL"="Jobs Act only X Large Firms",
                               "dd:SizeL"="Dignity Decree X Large Firms",
                               
                               "fa:SizeL:WorkTimeP"="Fornero Reform X Large Firms X Part-Time",
                               "jahi:SizeL:WorkTimeP"="Hiring Incentives X Large Firms X Part-Time",
                               "jao:SizeL:WorkTimeP"="Jobs Act only X Large Firms X Part-Time",
                               "dd:SizeL:WorkTimeP"="Dignity Decree X Large Firms X Part-Time"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |Post-reforms and worktime-reforms interactions coefficients excluded from the table 
        |Full-time worktime category is excluded as it is the reference group",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")))
kbl(WI, escape = F, align = "c")

```

### Did Interaction Summary Worker Features 3x2 segments

Table 5

```{r results = "asis"}

MFI <- htmlreg(list(FEdOECF,FEdOECY,FEdOECG, FEdFTCF,FEdFTCY,FEdFTCG), 
        digits =3,
        custom.model.names = c("Sex", "Age Group", "Geo Area", "Sex", "Age Group", "Geo Area"),
        custom.coef.map = list(
                               
                               # "fa:SizeL"="Fornero Reform X Large Firms",
                               # "jahi:SizeL"="Hiring Incentives X Large Firms",
                               # "jao:SizeL"="Jobs Act only X Large Firms",
                               # "dd:SizeL"="Dignity Decree X Large Firms",
                               
                               "fa:SizeL:SexF"="Fornero Reform X Large Firms X Female",
                               # "jahi:SizeL:SexF"="Hiring Incentives X Large Firms X Female",
                               "jao:SizeL:SexF"="Jobs Act only X Large Firms X Female",
                               "dd:SizeL:SexF"="Dignity Decree X Large Firms X Female",
                               
                               "fa:SizeL:AgeGroup<35"="Fornero Reform X Large Firms X Young",
                               # "jahi:SizeL:AgeGroup<35"="Hiring Incentives X Large Firms X Young",
                               "jao:SizeL:AgeGroup<35"="Jobs Act only X Large Firms X Young",
                               "dd:SizeL:AgeGroup<35"="Dignity Decree X Large Firms X Young",
                               
                               "fa:SizeL:AgeGroup35-54"="Fornero Reform X Large Firms X Prime Age",
                               # "jahi:SizeL:AgeGroup35-54"="Hiring Incentives X Large Firms X Prime Age",
                               "jao:SizeL:AgeGroup35-54"="Jobs Act only X Large Firms X Prime Age",
                               "dd:SizeL:AgeGroup35-54"="Dignity Decree X Large Firms X Prime Age",
                               
                               "fa:SizeL:GeoAreaSouth and Islands"="Fornero Reform X Large Firms X South and Islands",
                               # "jahi:SizeL:GeoAreaSouth and Islands"="Hiring Incentives X Large Firms X South and Islands",
                               "jao:SizeL:GeoAreaSouth and Islands"="Jobs Act only X Large Firms X South and Islands",
                               "dd:SizeL:GeoAreaSouth and Islands"="Dignity Decree X Large Firms X South and Islands",
                               
                               "fa:SizeL:GeoAreaCentral"="Fornero Reform X Large Firms X Central Italy",
                               # "jahi:SizeL:GeoAreaCentral"="Hiring Incentives X Large Firms X Central Italy",
                               "jao:SizeL:GeoAreaCentral"="Jobs Act only X Large Firms X Central Italy",
                               "dd:SizeL:GeoAreaCentral"="Dignity Decree X Large Firms X Central Italy"),
                               
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |Post-reforms, and control interactions coefficients, including dummy-reform or firmsize-reform interactions, not reported in the table|Each column exclude the reference category. Reference categories are respectively male, old age workers (55+ years old), and Northern Italy.",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES","YES","YES")),
        custom.header = list("Outcome Variable: OECs Growth" = 1:3,
                             "FTCs Growth" = 4:6),
        stars = c(0.001,0.01,0.05,0.1),
        include.aic = FALSE,
        include.loglik = TRUE,
        include.lr = TRUE)

kbl(MFI, escape = F, align = "c")

```


### DID Summary Position Features 2x2 other segments

Table 6

```{r results = "asis"}

SFI <- htmlreg(list(FEdOECPL,FEdOECPT,FEdFTCPL,FEdFTCPT ), 
        digits =3,
        custom.model.names = c("Position", "Worktime", "Position", "Worktime"),
        custom.coef.map = list(
                               
                               # "fa:SizeL"="Fornero Reform X Large Firms",
                               # "jahi:SizeL"="Hiring Incentives X Large Firms",
                               # "jao:SizeL"="Jobs Act only X Large Firms",
                               # "dd:SizeL"="Dignity Decree X Large Firms",
                               
                               "fa:SizeL:PositionBlueCollar"="Fornero Reform X Large Firms X Blue Collar",
                               # "jahi:SizeL:PositionBlueCollar"="Hiring Incentives X Large Firms X Blue Collar",
                               "jao:SizeL:PositionBlueCollar"="Jobs Act only X Large Firms X Blue Collar",
                               "dd:SizeL:PositionBlueCollar"="Dignity Decree X Large Firms X Blue Collar",
                               
                               "fa:SizeL:PositionWhiteCollar"="Fornero Reform X Large Firms X White Collar",
                               # "jahi:SizeL:PositionWhiteCollar"="Hiring Incentives X Large Firms X White Collar",
                               "jao:SizeL:PositionWhiteCollar"="Jobs Act only X Large Firms X White Collar",
                               "dd:SizeL:PositionWhiteCollar"="Dignity Decree X Large Firms X White Collar",
                               
                               "fa:SizeL:WorkTimeP"="Fornero Reform X Large Firms X Part-Time",
                               # "jahi:SizeL:WorkTimeP"="Hiring Incentives X Large Firms X Part-Time",
                               "jao:SizeL:WorkTimeP"="Jobs Act only X Large Firms X Part-Time",
                               "dd:SizeL:WorkTimeP"="Dignity Decree X Large Firms X Part-Time"),
        custom.note = "Standard errors in parentheses *** p < 0.001; ** p < 0.01; * p < 0.05 |Post-reforms, and control interactions coefficients, including dummy-reform or firmsize-reform interactions, not reported in the table|Each column exclude the reference category. Reference categories are respectively High White Collars and Full-Time workers",
        custom.gof.rows = list("Month FE" = c("YES","YES","YES","YES"),
                               "Year FE" = c("YES","YES","YES","YES"),
                               "Cell FE" = c("YES","YES","YES","YES"),
                               "Region SE Clustering" = c("YES","YES","YES","YES")),  
        custom.header = list("Outcome Variable: OECs Growth" = 1:2,
                             "FTCs Growth" = 3:4))

kbl(SFI, escape = F, align = "c")

```

# Appendix: Code used in this report 

Appendix

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE}
```

**R version and packages used**

```{r results = "asis"}
# print R version and packages
sessionInfo()
```
